Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
a

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "Goettingen"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
---

@@

## Global knowledge production and library catalogues

@@

**Overcoming a national gaze** focus on knowledge production through more complex cross-national networks

@@

- 900,000+ books and monographies (printed and electronic; 1488-)
- 70,000+ continuous publications (journals or series; 1771-)
- Series, maps, audiovisual, electronic material
- `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828

@@

- `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
- Altogether > 18 million entries

@@

**Open source** fully transparent and reproducible data analytics; every single detail, from raw data to final visualization https://github.com/rOpenGov/fennica

@@

## Analyse & Visualize

**Fast time line analysis**

```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
library(bibliographica)
titlecount_timeline(subset(df0, catalog == "Fennica"), 
          "publisher", nmin = 500, mode = "n")$plot
```

### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828

1) General trends & political events

2) Publishers in Sweden and Turku

3) Languages & religious texts in Finland

4) University curriculum & Enlightenment in Finland

Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.

>>>>

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
---

@@

## From particular data to global perspective?

@@

**Overcoming a national gaze** by focus on knowledge production through more complex cross-national network of cities

@@

- `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828

@@

- `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828

- **Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828**

@@

**Open source** fully transparent and reproducible data analytics: https://github.com/rOpenGov/fennica

@@
